
\documentclass[11pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}  % For footer customization

% Set up fancy page style
\pagestyle{fancy}
\fancyhf{} % Clear all header/footer fields
\renewcommand{\headrulewidth}{0pt} % Remove header rule
\fancyfoot[C]{\thepage} % Center page number in footer
\setlength{\footskip}{10pt}  % Increase space between text and footer

% Define bullet style
\setlist[itemize]{label=\textbullet, itemsep=0.2\baselineskip, parsep=0.2\baselineskip}

% Define section format
\titleformat{\section}[hang]{\bfseries}{}{0em}{}[\hrule]

% Define subsection format
\titleformat{\subsection}[hang]{\normalfont\large\bfseries}{}{0em}{\hspace{8em}}[\hrule]

% Adjust spacing above and below sections
\titlespacing*{\section}{0pt}{\baselineskip}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{0.25\baselineskip}{0.125\baselineskip}

% Custom sublist environment for subsections
\newlist{sublist}{itemize}{1}
\setlist[sublist]{label=\textbullet, nosep, leftmargin=1.5em, labelindent=0.5em, itemsep=0.1\baselineskip, parsep=0.2\baselineskip, topsep=0.3\baselineskip}

\begin{document}

\begin{center}
\textbf{\LARGE Jeong-Wan Choi}
\end{center}

\begin{center}
9 Courtyard Pl, Lexington, MA $|$ choiqz@bc.edu $|$ (781) 860-3176 $|$ linkedin.com/in/jeongwan-choi 
\end{center}

\section*{EDUCATION}
\textbf{Boston College, Morrissey College of Arts and Sciences;} Chestnut Hill, MA \\
\textit{Bachelor of Arts in Computer Science} \hfill \textbf{Expected May 2025} \\
GPA: 3.6/4.00 \\
Relevant Coursework: Data Structures \& Algorithms, Algorithms, Computer Systems, Logic \& Computation, Randomness \& Computation, Biomedical Image Analysis 

\section*{TECHNICAL SKILLS}
\textbf{Languages/Frameworks:} Python, .NET/C\#, NUnit, Selenium, Django, Java, SQL, Flask, JavaScript, \\
HTML/CSS \\
\textbf{Tools:} Linux, Gerrit, Jenkins, Neovim, Jinja, Git, BitBucket 

\section*{WORK EXPERIENCE}
\textbf{enLabel Global Services;} \textit{Software Development Intern} \hfill \textbf{June 2024 - Aug 2024}
\begin{sublist}
	\item Developed and maintained automated test suites using .NET/C\# and NUnit, reducing IPM Selenium build failures by more than 40\%. 
	\item Collaborated with the development team to integrate automated tests into the CI/CD pipeline, enhancing software delivery process and accelerating deployment times.
\end{sublist}

\raggedright
\textbf{Boston College IT Department;} \textit{Software Development Intern} \hfill \textbf{July 2023 - May 2024}
\begin{sublist}
	\item Created secondary password web-service using Python Flask and Jinja templating that returns back-up codes for users locked out of their accounts. 
	\item Built a modular DB CRUD interface handling suspended users and displaying their status using Flask, SQL, HTML/CSS.
\end{sublist}

\raggedright
\textbf{Boston College CS Department;} \textit{Teaching Assistant} \hfill \textbf{Jan 2023 - May 2023}
\begin{sublist}
	\item Helped students in Data Structures \& Algorithms (CSCI 1102) learn Java and object-oriented programming. 
	\item Led weekly, hour-long discussion sections for 20+ students and weekly office-hour sessions for individualized assistance. 
\end{sublist}

\section*{PROJECTS}
\raggedright
\textbf{Green Campus Dining;}  \textit{Main Contributor} \hfill \textbf{Sept 2024 - Dec 2024}
\begin{sublist}
	\item Contributed towards a group Django project aimed at incentivizing BC students to use sustainable dining practices.
	\item Spearheaded significant UI changes to core features: navigation, profile, and rewards.
\end{sublist}

\raggedright
\textbf{Slumbermeter;}  \textit{Main Contributor} \hfill \textbf{Sept 2024 - Dec 2024}
\begin{sublist}
	\item Designed a web page to track sleep quality across time using raw JavaScript, HTML/CSS with other group members.
	\item Implemented an algorithm that generates a sleep score based on user-inputted data and bedtime routine.
\end{sublist}

\section*{HONORS}
2021 NSDA Medal of Superior Distinction (top 2\% HS Debate), 2021 Gold President’s Volunteer Service Award, 2021 AP Scholar with Distinction

\end{document}
